X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-03-04 hedpc.tex
added G012 / to image 2

High-energy Talbot interferometry has been reported so far using a
synchrotron source at nominal energies of
$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013}. Using a low-brilliance
X-ray tube, Talbot-Lau interferometry was applied so far at
$\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}. Medical imaging
applications may benefit from phase contrast at higher energies: chest or
abdominal radiography or \ac{CT} require an acceleration voltage between
\num{100} and $\SI{150}{\kilo\voltpeak}$. Other potential applications are
homeland security or chip failure analysis, which require high energies for
the visualization of materials of high density and atomic number.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can absorb more than \SI{90}{\percent} of the incoming X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. The beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. From top to bottom, one source grating, two
        phase gratings and two analyzer gratings. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}\label{Fig:grating_mask}
\end{figure}

@@

\bibitem{Donath2009}
\bibinfo{author}{Donath, T.} \emph{et~al.}
\newblock \bibinfo{title}{{Inverse geometry for grating-based x-ray
  phase-contrast imaging}}.
\newblock \emph{\bibinfo{journal}{Journal of Applied Physics}}
  \textbf{\bibinfo{volume}{106}}, \bibinfo{pages}{054703}
  (\bibinfo{year}{2009}).

>>>>

High-energy Talbot interferometry has been reported so far using a
synchrotron source at nominal energies of
$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013}. Using a low-brilliance
X-ray tube, Talbot-Lau interferometry was applied so far at
$\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009a}. Medical imaging
applications may benefit from phase contrast at higher energies: chest or
abdominal radiography or \ac{CT} require an acceleration voltage between
\num{100} and $\SI{150}{\kilo\voltpeak}$. Other potential applications are
homeland security or chip failure analysis, which require high energies for
the visualization of materials of high density and atomic number.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can absorb more than \SI{90}{\percent} of the incoming X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. The beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. From top to bottom, one source grating, two
        phase gratings and two analyzer gratings. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. Multiple gratings for more than one setup
        geometry are fabricated on a single wafer.
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}\label{Fig:grating_mask}
\end{figure}

@@

\bibitem{Donath2009a}
\bibinfo{author}{Donath, T.} \emph{et~al.}
\newblock \bibinfo{title}{{Phase-contrast imaging and tomography at 60 keV
  using a conventional x-ray tube source.}}
\newblock \emph{\bibinfo{journal}{The Review of scientific instruments}}
  \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{053701}
  (\bibinfo{year}{2009}).
